---
title: ""
author: ""
email: ""
institute: ""
longinstitute: ""
web: ""
logo: ""
backimg: ""
bibliofiles: ""
posteroptions: width=90,height=110,scale=1.2 #,grid # portrait
headerheight: 13cm
colorstyle:
# large, Large, LARGE, huge, Huge, veryHuge, VeryHuge, VERYHuge
titlefont: size=\veryHuge,series=\bfseries
authorfont: size=\huge
institutefont: size=\Large
knit: (function(input, encoding, make = TRUE) { source('tex/makefile-renderer.R', local = TRUE) })
---

%% smart
%% to=latex
%% template=tex/poster.tex
%% filter=tex/poster-filters.py
%% biblatex

```{r packages-and-options, cache=FALSE}
library('ggplot2')
library('knitr')
theme_set(theme_grey(base_size=10))
knitr::opts_chunk$set(fig.width = 16, fig.height = 4)
```

[columns=2]

[column]

# Syntax help

### List:

- `citation` [@R-bdp]
- **bold**, _italic_, ` code`
- [Hyperlink](https://github.com/dapengde/bookdown-plus/archive/master.zip) and footnote^[This is a footnote].

### Numbered list:

- Units like \pps{900}
- Standard abreviations \\eg and \\ie for \eg and \ie
- \LaTeX
- vertical and horizontal blanks: \hfill1.5cm \vskip1.5cm

### Figures:

```{r co2, cache = TRUE, echo = FALSE, fig.cap='Carbon dioxide concentration, observed at Mauna Loa.'}
plot(co2)
```

### Tables:

header x  header y
--------- ----------
x1        y1
x2        y2


```{r tab1, tidy=FALSE, echo=FALSE}
knitr::kable(
  head(iris, 3), caption = 'IRIS data as an example.',
  booktabs = TRUE
)
```

### Invisible parts

<!--
comments
-->


[column]

# Introduction

### Motivation

### Objectives


# Methods

# Results


# Conclusions


# Take-home message

# Acknowledgements

# Bibliography

\printbibliography

[/columns]
